%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend developer, DevOps lead} % Job title
    {Order Spark} % Organization
    {Remote, USA (Freelance)} % Location
    {Oct. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building customer account API...}
        \item {Implemented Sentry error reporting on all systems.}
        \item {Organized, secured, cleaned up and documented system resources.}
        \item {Organized and documented API endpoints.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Web Developer} % Job title
    {One Potato, Ltd} % Organization
    {Remote, USA (Freelance)} % Location
    {Oct. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setup a staging server/environment.}
        \item {Redesigned the deliveries page.}
        \item {Fixed frontend VueJS bugs.}
        \item {Refactored and cleaned up parts of the codebase.}
        \item {Developed a weekly total billing component.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer, DevOps} % Job title
    {American National Hockey League.} % Organization
    {Remote, USA} % Location
    {Jan. 2022 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Debugging and maintaining a Django based admin panel.}
        \item {Connecting uploaded audio file briefs to AWS S3 with Amazon Alexa.}
        \item {Maintaining deployments on Heroku.}
        \item {Audited and mitigated unnoticed security advisories.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer, DevOps Assist} % Job title
    {Shyfter, SRL.} % Organization
    {Brussels, Belgium} % Location
    {Feb. 2021 - March 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated government services with compliance to security requirements like Dimona and audited and mitigated unnoticed security advisories.}
        \item {Advised and moved the company's backend from serverless Google Cloud Run to Google dedicated servers which resulted in a faster performance and response time as well as to GitHub for a more streamlined deployment pipeline and CD productivity.}
        \item {Worked on customer exclusive features and requirements.}
        \item {Built Redis based queue system and moved long processing operations to background jobs.}
        \item {Migrated legacy codebase from pure procedural PHP to resusable service classes resulting maintainability.}
        \item {Refactored code base reducing algorithmic complexity and also enforced coding standards for consistency.}
        \item {Built a printable dynamic GATT documents and assisted frontend team on API consumption.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack web developer} % Job title
    {Salesforce, Inc} % Organization
    {San Francisco, California} % Location
    {June. 2021 - December 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote the full test-suite for Unit, Feature and Browser QA tests.}
        \item {Developed and maintained CI/CD pipeline on GitHub with actions and Heroku deployments as well as review apps on branches connecting everything to Jira development board.}
        \item {Audited and mitigated unnoticed security advisories.}
        \item {Built Redis based queue system and moved long processing operations to background jobs.}
        \item {Worked on end-to-end features as part of a larger team, took responsibility of instantly pushing bug fixes as they arrive on Sentry and Bugsnag.}
        \item {Building campaign manager assets through Cloudinary API was dying in the background and it was hard to debug and tell what went wrong, I integrated Laravel Horizon \& a queue worker dyno on Heroku that immensely helped developers maintain a healthy codebase.}
        \item {Managers had the futile task of manually inviting users from Salesforce CRM to the campaign builder, I wrote a script to parse users export as CSV files, I created an admin panel where a manager can upload the CSV and it send out email invitations for people to register and because the project is deployed in the Heroku platform that Salesforce owns, I wrote a bash script to execute seeders and artisan commands on the release phase.}
        \item {Users leave their campaign builder form open in the office so I wrote a frontend code to detect inactivity and send an API request to auto logout and invalidate session (saving current unsubmitted work) at a configurable interval.}
        \item {Added a way for managers to flag users as (free access) so they don't get charged via Stripe.}
        \item {Sometimes logos get rendered incorrectly on top of certain backgrounds, I used Cloudinary API to intelligently invert or place the logo on a proper background.}
        \item {Certain developers and HTML designers kept on misspelling the brand name Salesforce, so I created a GitHub action that combs through the entire codebase and automatically correct the spelling with a bash script that uses grep and sed.}
      \end{cvitems}
     }

%---------------------------------------------------------
  \cventry
    {Co-Founder, CTO and Lead Developer} % Job title
    {Zidweb, LLC.} % Organization
    {Oran, Algeria} % Location
    {Feb. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provisioned an easily manageable hybrid infrastructure(Digital Ocean Droplets + On-premise) utilizing IaC tools like Sentry and OpenVPN}
        \item {Manage all DevOps and third party services integration (CloudFlare, Forge, Algolia, Pusher, Vonage)}
        \item {Implemented, documented RESTful API server for directory listing application}
        \item {Wrote and deployed several small scale apps like shopping carts.}
        \item {Restructured a +40 million records database of automotive spare parts catalog and implemented a web interface for it}
        \item {Created Backend in Laravel + Frontend in NuxtJS for an ELO Boosting gaming service.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full stack Software Engineer} % Job title
    {Didata LLC.} % Organization
    {Zürich, Switzerland} % Location
    {March. 2020 - April. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote example testing data seeders for BioLab research application}
        \item {Implemented an ACL architecture for Backend API}
        \item {Wrote mutations mapping module for state management following the Flux pattern for the Frontend application}
        \item {Implemented several CRUD models}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack web developer} % Job title
    {A-Tech Solutions LLC.} % Organization
    {Algiers, Algeria} % Location
    {Jan. 2019 - March. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote an HRM Module in ASP.NET Core for an ERP Platform}
        \item {Ported an existing application to Linux environment}
        \item {Wrote a CRUD view module in AngularJS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder and Lead Developer} % Job title
    {Bitshopit} % Organization
    {Algiers, Algeria} % Location
    {Apr. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {FIFA 2018 video streaming site, implemented RTMP, Redis queues, ffmpeg encoding, VideoJS HLS and Google IMA VAST}
        \item {Database architecture, business logic and API integration of Binance cryptocurrency exchange platform}
      \end{cvitems}
    }

\end{cventries}
